\cvsection{Highlights}

Seasoned software engineering leader with \textbf{15+ years} of experience, spanning roles from \textbf{technical co-founder} to \textbf{CTO} and \textbf{VP of Technology}. Leveraging a strong foundation in \textbf{mathematics and computer science} to design and implement scalable, high-performance systems. Proficient in multiple tech stacks including \textbf{Java, Python, and TypeScript}. Proven track record of fostering \textbf{continuous improvement} and \textbf{collaboration} through agile methodologies.

\vspace{2cm}

\cvsection{Latest Professional Experience}
\cvexpericence{Senior Software Engineer}{Spotify}{(5 years) December 2019 -- Present}{Stockholm, Sweden}
\bigskip

\begin{itemize}
    \item I joined \textbf{Spotify} in 2019, initially as a \textbf{consultant}, before transitioning to a \textbf{full-time employee} after a few months.
    \item My first mission was to:
    \begin{itemize}
        \item \textbf{Mentor} and \textbf{lead} a team of engineers in replacing a \textbf{legacy admin dashboard} with new technologies while modernizing and innovating the product.
        \item Successfully taught \textbf{TypeScript} and \textbf{React} to the team while creating a new \textbf{microservice-based architecture} using \textbf{async Python}.
        \item Innovated by developing a new \textbf{transport protocol} for \textbf{low latency} and \textbf{high reliability}.
        \item Delivered a product that has been in successful use and continuous development for five years, with virtually no tech-related incidents.
        \item Established close collaboration with our \textbf{stakeholders} and \textbf{users}, conducting numerous \textbf{user studies} and utilizing Spotify's then-new \textbf{design language} to deliver a highly usable product.
    \end{itemize}

    \item During my tenure with the team, I was responsible for:
    \begin{itemize}
        \item Defining, prioritizing, and leading \textbf{tech initiatives}.
        \item Creating a collaborative setup and running \textbf{tech retrospectives} to reduce \textbf{technical debt} and maintain high-quality services with low maintenance effort.
        \item Leading and educating the team on the importance of \textbf{SLIs} and \textbf{SLOs} for reliability and quality.
        \item Implementing our first \textbf{SLOs} and establishing a weekly meeting to review our \textbf{SLOs} and other reliability-related dashboards, fostering a culture of \textbf{continuous improvement}.
    \end{itemize}
    \item Before moving on to my next stop at Spotify, I was responsible for \textbf{onboarding} and mentoring the new team replacing us, ensuring their success.
\end{itemize}

\newpage
\cvsection{Latest Professional Experience}
\cvexpericence{Senior Software Engineer}{Spotify}{(5 years) December 2019 -- Present}{Stockholm, Sweden}
\bigskip

\begin{itemize}

    \item My next journey at Spotify involved:
    \begin{itemize}
        \item Transforming the \textbf{Customer Support tooling} Product Area into a \textbf{platform}.
        \item Leading the effort to define and implement a new product as the first successful example of a platform for our product area.
        \item Leading a team of senior engineers in an \textbf{RFC-driven approach}.
        \item Establishing close relationships with stakeholders and designers to identify needs and progress through different \textbf{MVP phases} to launch a full product.
        \item Coordinating and collaborating with stakeholders, negotiating requirements and timelines, defining roadmaps, and ensuring we met our commitments.
        \item Focusing on \textbf{reliability}, \textbf{scalability}, and \textbf{extensibility} to create a platform that easily onboards new lines of business and customer channels while streamlining integration with third-party vendors used by Customer Support.
    \end{itemize}

    \item After leading the initial definition, design, and launch of the product, I took ownership of the \textbf{frontend} component and:
    \begin{itemize}
        \item Mentored my team in frontend technologies while actively contributing to other areas.
        \item Led an initiative to reduce the number of \textbf{PagerDuty alerts} from our legacy systems by implementing a \textbf{data-driven approach}.
        \item Created metrics on alert frequency, sources, false positive rates, and categories.
        \item Guided the team in improving processes and enhancing our quality culture by conducting \textbf{post-mortems} for incidents and reducing alert noise.
        \item Successfully reduced PagerDuty alerts by over 80%.
    \end{itemize}

    \item My latest focus is on the \textbf{reliability working group} of our product area, of which I am a founding member. Our first initiative, which has become a product area-wide effort with TSG approval, was to generate our first-ever \textbf{monthly availability report} for our product area.
\end{itemize}